STAT 450 Project: Real Estate

### 2020-03-31 src/2nd_draft.Rmd
fix typo

Other than ordinary linear regressions, we are also interested in the performance of more advanced linear regressions like *Ridge* and *Lasso*. *Ridge* and *Lasso* have different objective functions to optimize; they take penalties in the sum of absolute values and sum of squared absolute values of weights respectively. A reason to consider Ridge Regression is that it helps deal with multicollinearity of the explanatory variables. This might be relevant to our study as some features used in this study are correlated (assessTotal, landTotal and improvementTotal). Lasso Regression is also included in this study because it does variable selections automatically by imposing a constraint on model parameters that possibably causes some regression coefficients to shrink to zero.

>>>>

Other than ordinary linear regressions, we are also interested in the performance of more advanced linear regressions like *Ridge* and *Lasso*. *Ridge* and *Lasso* have different objective functions to optimize; they take penalties in the sum of absolute values and sum of squared absolute values of weights respectively. A reason to consider Ridge Regression is that it helps deal with multicollinearity of the explanatory variables. This might be relevant to our study as some features used in this study are correlated (assessTotal, landTotal and improvementTotal). Lasso Regression is also included in this study because it does variable selections automatically by imposing a constraint on model parameters that may possibably causes some regression coefficients to shrink to zero.
